Computational Prediction of 3D Genomic Domains using 1D Genome Annotations

### 2019-07-22 Manuscript/manuscript_structured.Rmd
added prefered results for predicting boundaries at bp res

### Consider distance
-->

>>>>

### Consider distance

## Predicting at bp resolution

### Empirical way to determine boundary regions

### Predicted TAD boundary regions vs Called TAD boundary regions

#### Number of predicted regions compared to called regions
#### Overlap between the two
#### Summary statistics
##### Distribution of distances 
###### densities
###### ECDF
##### Jaccard indeces
##### Enrichment

-->
